### 2018-09-17 submission/supplemental.Rmd
update re sana re class

table_s3 <- temp_t3a %>%
  bind_rows(temp_t3b) %>%
  mutate(fstat = round(fstat, digits = 2),
         r2 = round(r2, digits = 3),
         pvalue = round(pvalue, digits = 4),
         study = c("Lu", "Flemer", "Lu (Matched)"),
         comparison = "Adenoma",
         sample_type = "Tissue") %>%
  select(study, comparison, sample_type, r2, pvalue)

@@

table_s4 <- temp_t4a %>%
  bind_rows(temp_t4b) %>%
  mutate(fstat = round(fstat, digits = 2),
         r2 = round(r2, digits = 3),
         pvalue = round(pvalue, digits = 4),
         study = c("Sanapareddy", "Burns", "Flemer", "Chen",
                   "Dejea (Matched)", "Geng (Matched)", "Burns (Matched)"),
         comparison = "Carcinoma",
         sample_type = "Tissue") %>%
  select(study, comparison, sample_type, r2, pvalue)

>>>>

table_s3 <- temp_t3a %>%
  bind_rows(temp_t3b) %>%
  mutate(fstat = round(fstat, digits = 2),
         r2 = round(r2, digits = 3),
         pvalue = round(pvalue, digits = 4),
         study = c("Lu", "Sanapareddy", "Flemer", "Lu (Matched)"),
         comparison = "Adenoma",
         sample_type = "Tissue") %>%
  select(study, comparison, sample_type, r2, pvalue)

@@

table_s4 <- temp_t4a %>%
  bind_rows(temp_t4b) %>%
  mutate(fstat = round(fstat, digits = 2),
         r2 = round(r2, digits = 3),
         pvalue = round(pvalue, digits = 4),
         study = c("Burns", "Flemer", "Chen",
                   "Dejea (Matched)", "Geng (Matched)", "Burns (Matched)"),
         comparison = "Carcinoma",
         sample_type = "Tissue") %>%
  select(study, comparison, sample_type, r2, pvalue)
